% Problem formulation,  project roadmap, Explanation of roles assigned to each member and the contributions 

\section{Introduction}
\textit{Siddharth}: "I suggested this project because its really close to my heart and something I've experienced. Cardiac arrest runs in my family, and I’ve lost four loved ones to it in the past 5 years. This project could provide valuable insights and predictions that might help people prepare for the future and potentially avoid the same fate. Not everyone knows that they are suffering from a heart condition until it is too late, and I wished to avail myself of the opportunity to give others a feeling of relief and awareness about their health. This project, in itself, has been a relief for me something I could do to help, even though I couldn't save my loved ones. I may not be able to prevent what happened , but with this, I can help prevent more incidents save a few tears." 

Cardiovascular disease continues to be a critical global health issue, representing a substantial share of death and morbidity globally. Timely identification and treatment are essential in alleviating the impact of cardiac disease, enabling prompt therapies that enhance patient outcomes. The diagnosis of cardiac disease conventionally depends on clinical competence, laboratory analyses, and imaging examinations. Nonetheless, these methods may be laborious, resource-demanding, and susceptible to human mistake. With the increasing amount and complexity of healthcare data, machine learning (ML) presents a viable approach to improve diagnostic procedures by automating risk prediction and revealing patterns that may not be readily discernible to doctors.

Machine learning models are proficient in processing intricate datasets, making them suitable for addressing the complexities of heart disease detection. These models may analyze previous data to forecast future results, discern critical risk variables, and facilitate decision-making in healthcare environments. This research intends to use machine learning methodologies to develop a prediction model for heart disease risk, using the Cleveland Heart Disease Dataset. This dataset encompasses several patient features, including demographic data, clinical measures, and test results, making it suitable for machine learning research.

To successfully tackle the issue, we will examine and contrast three prominent machine learning algorithms: Logistic Regression, Random Forest, and Artificial Neural Networks. These models are selected for their unique advantages and their prevalent use in classification tasks. Logistic Regression offers a straightforward and comprehensible framework for elucidating the associations between characteristics and the probability of heart disease. Random Forest provides strong performance and the capacity to identify intricate, nonlinear relationships among variables. Artificial Neural Networks, recognized for their proficiency in managing high-dimensional datasets, excel at identifying decision boundaries that delineate classes.

Metrics for evaluation, including accuracy, precision, recall, and F1 score, will inform the assessment of these models. Cross-validation will be used to guarantee that the results generalize well to novel data, fulfilling the essential criterion of dependability in medical applications. The use of these stringent assessment methods demonstrates the study's dedication to generating reliable and replicable outcomes.

The comparative examination of Logistic Regression, Random Forest, and Artificial Neural Networks offers a comprehensive view of machine learning applications in healthcare. Logistic Regression is chosen for its interpretability, which is essential for clinical use. Its capacity to provide obvious, measurable correlations between traits and outcomes makes it especially appropriate for elucidating findings to non-technical audiences, including healthcare practitioners. Conversely, Random Forest demonstrates resilience to overfitting and is proficient in identifying complicated nonlinear relationships among variables, making it suitable for datasets with elaborate patterns. Artificial Neural Networks have exceptional proficiency in modeling high-dimensional and complicated data, however they face issues with interpretability and processing demands.

The primary objective of this study is to use machine learning models to forecast the occurrence of heart disease based on critical attributes in the dataset. Through the assessment and comparison of these models' performance, we want to determine the most effective algorithm while acquiring insights into the use of machine learning in healthcare data. This study advances the expanding domain of predictive analytics in healthcare, highlighting the capacity of data-driven methodologies to enhance patient care and results.

