\section{Contributions}

\subsection{Anirudh Basu}
Anirudh contributed to the final report by completing the exploratory data analysis (EDA), artificial neural network model, and creating the web app. In the EDA section, Anirudh analyzed the dataset, identifying the distribution of features, and the correlation between them. In the artificial neural network model section, Anirudh implemented the model, trained it, and evaluated its performance. In the web app section, Anirudh created a web app using Flask, which allows users to input patient data and get predictions on the likelihood of a cardiovascular disease diagnosis.

\subsection{Bipasha Sengupta}
Bipasha contributed to the final report by completing the introduction, literature review, and conclusion parts. In the introduction, Bipasha delineated the importance of predicting cardiovascular illness and the contribution of machine learning models in improving diagnostic methods. The literature study highlighted the use of Logistic Regression, Random Forest, and Artificial Neural Networks (ANNs), accentuating their advantages and pertinence to our project. Bipasha also added to the model comparison. In the end, Bipasha consolidated the results, emphasizing the potential of artificial neural networks (ANNs) to tackle intricate, high-dimensional medical datasets, while proposing future avenues for improving interpretability and therapeutic relevance.

\subsection{Jhaydine Bandola}
Jhaydine contributed to the final report by completing the logistic regression model, which included building both a baseline model and a tuned model. Jhaydine trained each model using the dataset and evaluated their performances through metrics such as the Confusion Matrix and Receiver Operating Characteristic (ROC) curve. Jhaydine analyzed the precision, recall, accuracy, and AUC (Area Under the Curve) values provided by these metrics to thoroughly assess the effectiveness of the models. Her analysis ultimately concluded that logistic regression is a reliable and interpretable approach for predicting heart disease.

\subsection{Siddharth Singh Killedar}
Sid worked on building the Random Forest model to predict heart disease and focused on understanding the dataset, ensuring proper preprocessing and feature engineering. Initially, Sid experimented with hyperparameter tuning but found better results using cross-validation, which improved the model's accuracy. Understanding the dataset was initially challenging, but with the team's support and insights, Sid was able to navigate through it effectively. Sid also contributed to interpreting the model's results to ensure they aligned with our project goals.

\textit{Team Leader Notes}: Our team made collaboration feel seamless and natural. We spent time studying and working together, bouncing ideas off each other, and refining our approach through open discussions. Everyone communicated well and responded promptly to tasks, creating an environment where we could learn and grow together. This shared energy and dedication made the project not only successful but also an enjoyable learning experience.

\subsection{William Popov Spektor}
William contributed to the final report by drafting the abstract, introduction, dataset, and models sections, ensuring any reader could clearly understand each written section. William also edited the entire document, changing layouts, grammar and structure, as well as the overall flow of material. Additionally, William helped in selecting the three models, providing insights into the benefits and drawbacks of all discussed models, eventually helping the group come to the conclusion: Logistic Regression, Random Forest, and Artificial Neural Networks.


\textit{Note from the entire team}: Our project could not have been completed without the collective efforts and commitment of our team members. Every member provided distinct abilities and viewpoints, enabling us to tackle issues innovatively and efficiently. We had a very supportive team leader too. From data preparation and exploratory analysis to model creation and assessment, all participants showed remarkable dedication to the project's success.
The team's collaborative attitude and excitement fostered an atmosphere of mutual support and ongoing growth. This experience enhanced our technical expertise and fortified our capacity for collaborative work. We express our profound appreciation to our team members for their essential contributions and steadfast commitment to our project.
